---
title: "Grammatical Evolution of pyramid schemes in smart contract environment 3.0"
author: "Peter Fratric"
date: "1/17/2022"
output: html_document
---

```{r setup, include=FALSE}
setwd("/home/peter/Desktop/phd/evolutionaryComputation/Coine")
knitr::opts_chunk$set(echo = TRUE)
library("gramEvol", quietly = TRUE)
library(RecordLinkage, quietly = TRUE)
library("parallel", quietly = TRUE)
library(ggplot2, quietly = TRUE)
library(igraph, quietly = TRUE)
set.seed(319)
```

# ABM for Ponzi scheme siumulation

## Initialization

```{r init}
#ABM initialization (global variables)
Nagents <- 100 + 1
entry_fee <- rlnorm(Nagents, meanlog = 1.5, sdlog = 0.7 )
entry_fee <- 10*rbeta(Nagents, 2, 2)
#entry_fee <- runif(Nagents, max = 1000)
#th <- runif(Nagents, min = 0, max = 1)
th <- entry_fee/max(entry_fee)
#initiator_balance: (should have a starting budget)
hist(entry_fee, breaks = 25, main = "entry_fee")
hist(th, breaks = 25, main = "trust thresholds")

#plot function
plotEvo <- function(title = ""){
  plot(100*(sort(agent_balance) - sort(entry_fee))/sort(entry_fee), 
       type = "l",
       main = paste0("capital distribution change", title),
       ylab = "money",
       xlab = "ordered agents by capital")
  #lines(sort(agent_balance[-Nagents]), col = "red")
}

append_file <- function(expr, expr_fitness, path = "/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt"){
  input <- data.frame("expression" = paste(as.character(expr), collapse = ","), "fitness" = expr_fitness)
  write.table(input, file=path, append = TRUE, sep = "|", row.names = FALSE, col.names = FALSE)
}
read_file <- function(path = "/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt"){
  df <- read.table(file=path, sep = "|")
  colnames(df) <- c("expr","fitness")
  return(df)
}

#capital distribution
plot(sort(entry_fee), main = "initial distribution of capital")
```

## Transaction graph actions

```{r graph_actions}
addNode <- function(node_id){
  if(length(node_id) > 1){
    initiator_balance <<- initiator_balance - 100
    stop(paste0(node_id," in addNode(node_id) is of lenght > 1"))
  }else if(node_id %in% V(g1)$name){
    initiator_balance <<- initiator_balance - 100
    stop(paste0(node_id," in addNode(node_id) is already in V(g1)$name"))
  }else{
    if(is.null(node_id)){
      initiator_balance <<- initiator_balance - 100
      stop("node_id in addNode(node_id) is NULL")
    }else{
      g1 <<- g1 + vertices(node_id)
    }
  }
}

addEdge <- function(node_id_from, node_id_to, weight){
  if(length(node_id_to) > 1){
    initiator_balance <<- initiator_balance - 100
    stop(paste0(node_id_to," in addEdge is of lenght > 1"))
  }else if(are.connected(g1, as.character(node_id_from), as.character(node_id_to)) == FALSE){
    g1 <<- add_edges(g1, c(node_id_from, node_id_to))
    g1 <<- set_edge_attr(g1, "weight", index = E(g1)[length(E(g1))], value = weight)
  }
}


# in order for this action to make sense, you need to introduce a premis that implicitly tells you there is an edge between two nodes
# e.g. if IDinProfit, then remove edge c(contract, ID); if lastUnpayed == TRUE: then remove edge c(contract, lastUnpayedID() )
# removeEdge <- function(node_id_from, node_id_to){
#   if(are.connected(g1, as.character(node_id_from), as.character(node_id_to)) == TRUE){
#     e <- data.frame(from = as.character(node_id_from), to = as.character(node_id_to))
#     e <- apply(e, 1, paste, collapse="|")
#     e <- edges(e)
#     g1 <<- g1 - e
#   }else{
#     #initiator_balance <<- initiator_balance - 100
#     #stop("vertecies are not connected in removeEdge")
#   }
# }

removeEdges <- function(node_ids){
  if(length(node_ids) > 0){
    for(node_id_to in node_ids){
      if(are.connected(g1, "contract", as.character(node_id_to)) == TRUE){
        e <- data.frame(from = "contract", to = as.character(node_id_to))
        e <- apply(e, 1, paste, collapse="|")
        e <- edges(e)
        g1 <<- g1 - e
      }
    }
  }
}

updateEdge <- function(node_id_from, node_id_to, new_weight){
  if(are.connected(g1, as.character(node_id_from), as.character(node_id_to)) == TRUE){
    e <- data.frame(from = as.character(node_id_from), to = as.character(node_id_to))
    e <- apply(e, 1, paste, collapse="|")
    e <- edges(e)  
    g1 <<- set_edge_attr(g1, "weight", index = e[[1]], new_weight)
  }
}
```


```{r graph_plot_pic}

plotG <- function(g = NULL, lyt=layout_as_star(g)){
  plot(g, layout = lyt, vertex.label.cex = 2, vertex.label.dist=2.5, edge.width = 2.5, edge.color = "black", edge.arrow.size = 1, edge.label = edge_attr(g1, "weight"), edge.label.cex = 2)
}

#jpeg(filename="graphinit.jpg", width = 3*300, height = 250)
par(mar = c(2, 2, 2, 2))
op <- par(mfrow=c(1,3))

n_tmp <- 6
g1 <- make_empty_graph(n_tmp)
V(g1)$name <- c("contract", "initiator",as.character(1:(n_tmp-2)))
V(g1)$color <- c("red", "red", rep("blue", n_tmp-2))
l <- layout_with_fr(g1) 
plotG(g1, l)
box(col = "grey", which = "figure")
addEdge(1, "contract", 11.15)
#E(g1)$weight <- edge_attr(g1, "weight")
plotG(g1, l)
box(col = "grey", which = "figure")
V(g1)$color <- c("red", "red", "red", rep("blue", n_tmp-3))

e <- data.frame(from = as.character(1), to = "contract")
e <- apply(e, 1, paste, collapse="|")
e <- edges(e)
g1 <<- g1 - e

plotG(g1, l)
box(col = "grey", which = "figure")
par(op)
#dev.off()
```

```{r abm}
penalty <- function(expr){
  return(0)
}

accept_vector <- rep(0, Nagents)
agent_balance <- rep(0, Nagents)
contract_balance <- 0.0
initiator_balance <- 0.0
g1 <- make_empty_graph(2)
V(g1)$name <- c("contract", "initiator")
addEdge("contract", "initiator", 0.5)

#ABM definition
ABM <- function(expr, writeToFile = TRUE, path = "/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt", toplot = FALSE, iterseq = NULL){
  #stats
  users_pop <<- c(0)
  #print(expr)
  #append_file(expr, 0, path = "/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprs.txt")
  
  #reorder the th vector so that the most gullible agents are at the start
  
  #entry_fee <<- sort(entry_fee)
  #th <<- entry_fee/max(entry_fee)

  #initialize global variables
  accept_vector <<- rep(0, Nagents)
  agent_balance <<- entry_fee
  contract_balance <<- 0
  initiator_balance <<- 0
  g1 <<- make_empty_graph(2)
  V(g1)$name <<- c("contract", "initiator")
  line_to_pay <<- NULL
  paying <<- NULL
  #addEdge("contract", "initiator", 0.5)
  #initialize local variables
  n_users <- 1
  contractID <- "contract"
  initiatorID <- "initiator"
  
  #Simulation
  steps <- 1
  maxsteps <- Nagents
  if(is.null(iterseq)){
    iterseq <- rep(TRUE, maxsteps)
  }

  new_accepts <- TRUE
  while(new_accepts == TRUE && steps < maxsteps){
    users_pop <<- c(users_pop, n_users)
    
    #calculate trust of a contract
    if(n_users > 0){
      tmp_profit <- agent_balance - entry_fee
      agents_in_profit <- which(tmp_profit > 0 & accept_vector == 1)
      trust_coef <- (1-penalty(expr))*((1+length(agents_in_profit))/n_users)*((n_users/Nagents)^Kpar) #1-exp(-1/101)
    }
    
    new_users <- which(trust_coef > th & accept_vector == 0)
    if(length(new_users) > 0){

      new_userID <- new_users[1]
      fee <- entry_fee[new_userID]
      contract_balance <<- contract_balance + fee
      agent_balance[new_userID] <<- agent_balance[new_userID] - fee
      n_users <- n_users + 1
      accept_vector[new_userID] <<- 1
      addToLine(new_userID)
      
      addNode(new_userID)
      
      #contract
      tryCatch(eval(expr), error=function(e){initiator_balance <<- initiator_balance - 100})
      #tryCatch(eval(expr), error=function(e){initiator_balance <<- initiator_balance - 100}, finally = {append_file(expr, initiator_balance);return(initiator_balance)})
      #tryCatch(eval(expr), error=function(e){print(e)})
      #print("running")
      tryCatch(graph_exec(), error=function(e){initiator_balance <<- initiator_balance - 100})
      #tryCatch(graph_exec(), error=function(e){print(e)})
      if(toplot == TRUE && iterseq[steps] == TRUE){
        lout <- layout_as_star(g1)
        plot(g1, layout = lout)
        box(col = "grey", which = "figure")
      }
    }else{
      #stopping condition
      new_accepts <- FALSE
    }
    steps <- steps + 1
  }
  if(writeToFile == TRUE){
    append_file(expr, initiator_balance, path)
  }
  return(initiator_balance)
}

#expr <- expression(if(TRUE) addNode(new_userID), if(TRUE) addEdge(contractID, new_userID, 0.5*contract_balance))
#ABM(expr = expr)
```


## transaction graph exectution

```{r transaction_graph}
graph_exec <- function(){
  #if(is.null(getLastSentID()) == FALSE){
  #  edge_id <- get.edge.ids(g1, c(getLastSentID(), "contract"))
  #  to_pay <- E(g1)[edge_id]$weight
  #  contract_balance <<- contract_balance + to_pay
  #  agent_balance[getLastSentID()] <<- agent_balance
  #}
  
  if(gsize(g1) > 0){
    ws <- E(g1)[from("contract")]$weight
    es <- adjacent_vertices(g1, "contract")$contract
    for(i in 1:length(ws)){
      to_pay <- ws[i]
      usr_to_id <- es[i]$name
      
      if(contract_balance - to_pay >= 0){
        if(usr_to_id == "initiator"){
          contract_balance <<- contract_balance - to_pay
          initiator_balance <<- initiator_balance + to_pay
        }else{
          usr_to_id <- as.numeric(usr_to_id)
          contract_balance <<- contract_balance - to_pay
          agent_balance[usr_to_id] <<- agent_balance[usr_to_id] + to_pay
          
          paying <<- paying + 1
          if(paying == length(line_to_pay) + 1){
            paying <<- 1
          }
          
        }
      }else{
        break
      }
    }
  }
}

```

# Generation of Ponzi schemes

expression(if (NUsersEq(2)) addEdge(contractID, initiatorID, 0.2 * getFee(new_userID)), if(TRUE) addNode(new_userID), if(BalanceFeeHigher(getNextToPay())) addEdge(contractID, getNextToPay(), 1.2 * getFee(getNextToPay())), if (TRUE) removeEdges(userInProfit()))

## Premises and --get-- methods

```{r factsandids}
#facts
BalanceFeeHigher <- function(node_id, wei){
  if(is.null(node_id)){
    initiator_balance <<- initiator_balance - 100
    stop("node_id in BalanceFeeHigher(node_id) is NULL")
  }else if(length(node_id) > 1){
    initiator_balance <<- initiator_balance - 100
    stop("node_id in BalanceFeeHigher(node_id) is of lenght > 1")
  }else if(node_id == "initiator"){
    initiator_balance <<- initiator_balance - 100
    stop("node_id in BalanceFeeHigher(node_id) is initiator")
  }else if(contract_balance >= wei){
    if(are.connected(g1, as.character("contract"), as.character(node_id)) == FALSE){
      return(TRUE)
    }
  }
  return(FALSE)
}

#get attributes
NUsersEq <- function(n){
  if(gorder(g1) == n + 2){
    return(TRUE)
  }
  return(FALSE)
}

getFee <- function(node_id){
  if(is.null(node_id)){
    initiator_balance <<- initiator_balance - 100
    stop("node_id in getFee(node_id) is NULL")
  }else if(length(node_id) > 1){
    initiator_balance <<- initiator_balance - 100
    stop(paste0(node_id," in getFee(node_id) is of length > 1"))
  }else if(node_id == "initiator"){
    initiator_balance <<- initiator_balance - 100
    stop(paste0(node_id," in getFee(node_id) is initiator"))
  }else{
    return(entry_fee[node_id])
  }
}

userInProfit <- function(){
  tmp_profit <- agent_balance - entry_fee
  tmp <- which(tmp_profit > 0 & accept_vector == 1)
  return(tmp)
}


#you need to extend the ABM to safe the order of arrival
line_to_pay <- NULL
paying <- NULL
addToLine <- function(new_user){
  if(length(line_to_pay) == 0){
    line_to_pay <<- c(new_user)
    paying <<- 1
  }else{
    line_to_pay <<- c(line_to_pay, new_user)
  }
}

getNextToPay <- function(){
  return(line_to_pay[paying])
}

getLastPaid <- function(){
  return(line_to_pay[paying - 1])
}

```

## Benchmark cases

TODO:
1. seems to work ok for waterfall, but with edgeUpdate would be better
2. seems to work ok for array scheme, but move if's from functions to grammar to make the logic more visible in the paper

```{r expressions}
Kpar <- 0.1

expr2 <- expression(if (NUsersEq(1)) addEdge(contractID, initiatorID, 0.5 * getFee(new_userID)), if(TRUE) addEdge(contractID, new_userID, 0.5 * getFee(new_userID)) )

ABM(expr2, writeToFile = FALSE, toplot = TRUE)
gorder(g1)
gsize(g1)
```

```{r exprArray}
# connectedUserInProfit
# if (BalanceFeeHigher(getNextToPay()) && disconnected)

#note that sometimes the edge for NextToPay agent is not executed for a longer time (2-3 images), but this is only because there is also an arrow for the initiator and so, after sending to initiator first, there might not be enough capital left for second transaction
expr3 <- expression(
  if (NUsersEq(1)) addEdge(contractID, initiatorID, 0.5 * getFee(new_userID)), 
  if(BalanceFeeHigher(getNextToPay(), 1.2*getFee(getNextToPay()))) addEdge(contractID, getNextToPay(), 1.2 * getFee(getNextToPay())), 
  if(TRUE) removeEdges(getLastPaid()))

ABM(expr3, writeToFile = FALSE, toplot = TRUE)
gorder(g1)
gsize(g1)
```

## Waterfall

```{r gramdef}
# terminals addEdge, removeEdge, addNode, Remove Node

#waterfall discovery
ruleDef <- list(start = gsrule("<clause>;<start>","<clause>"),
                clause = gsrule("if(<premise>) <action>"),
                #premise = gsrule("<fact>","<fact> && <premise>"),
                premise = gsrule("TRUE","NUsersEq(<int>)"),#, "BalanceFeeHigher(<node>)"),
                int = grule(1,2,3,4,5,10,50),
                action = gsrule("addNode(<node>)", "addEdge(contractID,<node>,<weight>)", "removeEdges(<node>)"),
                weight = gsrule("<mult>*getFee(<node>)", "<mult>*contract_balance"), 
                node = gsrule("new_userID", "initiatorID"),
                mult = grule(0.06, 0.1, 0.2, 0.5, 1.2, 2.0)
                )

grammarDef <- CreateGrammar(ruleDef)
grammarDef
GetGrammarNumOfExpressions(grammarDef, max.depth = 6)
GetGrammarMaxSequenceLen(grammarDef, max.depth = 6)
```


```{r}
#btw this works: eval(expression(print(1+5),print(5+5))) and has the same form as what goes from grammar expression(expr,expr,...,expr)

randExamples <- GrammarRandomExpression(grammarDef, 2, max.depth = 25)
randExamples
```

## Grammatical Evolution

```{r optevo}
fitness <- function(expr) {
  contract_owner_total <- ABM(expr)
  #return contract owner obtained total
  if(any(is.nan(contract_owner_total)))
    return(Inf)
  return(-contract_owner_total)
}

monitorFunc <- function(result) {
  if(result$population$currentIteration %% 50 == 0){
    cat("iteration", result$population$currentIteration, "Best of gen:", min(result$best$cost), "\n")
  }
}

gc()

if(file.exists("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")==TRUE){
  file.remove("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")
  file.create("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")
}else{
  file.create("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")
}

start.time <- Sys.time()
#cl <- makeCluster(6)
#clusterEvalQ(cl, library("gramEvol"))
#clusterEvalQ(cl, library("igraph"))
#clusterExport(cl, c("fitness","ABM","Nagents","entry_fee","th","penalty","append_file","make_empty_graph","V","addToLine"))
ge <- GrammaticalEvolution(grammarDef, fitness, terminationCost = -20, iterations = 100, max.depth = 6, popSize = 100, elitism = 0, monitorFunc = monitorFunc)#, plapply = function(...) parLapply(cl, ...))
#stopCluster(cl)
end.time <- Sys.time()

ge

time.taken <- end.time - start.time
time.taken

buffer_stack <- read_file()
plot(tail(sort(as.numeric(buffer_stack$fitness)),20), type = "l", main = "best 20 solutions")
```


```{r plot_prepare}
tmp <- which(as.numeric(buffer_stack$fitness) > 20)
length(tmp)
tmp <- as.numeric(buffer_stack$fitness)[tmp]
hist(tmp)
```

## Array-based scheme

expr3 <- expression(
  if (NUsersEq(1)) addEdge(contractID, initiatorID, 0.5 * getFee(new_userID)), 
  if(BalanceFeeHigher(getNextToPay(), 1.2*getFee(getNextToPay()))) addEdge(contractID, getNextToPay(), 1.2 * getFee(getNextToPay())), 
  if(TRUE) removeEdges(getLastPaid()))

```{r gramdef_extended}
# terminals addEdge, removeEdge, addNode, Remove Node

added_actions <-  "if(NUsersEq(1)) addEdge(contractID, initiatorID, 0.5 * getFee(new_userID)); 
  if(BalanceFeeHigher(getNextToPay(), 1.2*getFee(getNextToPay()))) addEdge(contractID, getNextToPay(), 1.2 * getFee(getNextToPay()))"


#added_actions <- "if(NUsersEq(1)) addEdge(contractID,initiatorID,<mult>*getFee(new_userID))"



#waterfall discovery
ruleDef_ext <- list(#init = gsrule(paste(added_actions,"<start>",sep = ";")),
                start = gsrule("<clause>;<start>","<clause>"),
                clause = gsrule("if(<premise>) <action>"),
                #premise = gsrule("<fact>","<fact> && <premise>"),
                premise = gsrule("TRUE","NUsersEq(<int>)","BalanceFeeHigher(<node>, <weight>)"),
                int = grule(1,2,3,4,5,10,50),
                action = gsrule("addNode(<node>)","addEdge(contractID,<node>,<weight>)", "removeEdges(<node>)"),
                weight = gsrule("<mult>*getFee(<node>)", "<mult>*contract_balance"),
                node = gsrule("new_userID", "initiatorID", "getNextToPay()", "getLastPaid()"),
                mult = grule(0.06, 0.1, 0.2, 0.5, 1.2, 2.0)
                )

grammarDef <- CreateGrammar(ruleDef_ext)
grammarDef
GetGrammarNumOfExpressions(grammarDef, max.depth = 10)
GetGrammarMaxSequenceLen(grammarDef, max.depth = 10)
```


```{r}
#btw this works: eval(expression(print(1+5),print(5+5))) and has the same form as what goes from grammar expression(expr,expr,...,expr)

randExamples <- GrammarRandomExpression(grammarDef, 5, max.depth = 9)
randExamples
```

## Grammatical Evolution

```{r optevo}
fitness <- function(expr) {
  contract_owner_total <- ABM(expr, path = "/home/peter/Desktop/phd/evolutionaryComputation/Coine/expr.txt")
  #return contract owner obtained total
  if(any(is.nan(contract_owner_total)))
    return(Inf)
  return(-contract_owner_total)
}

gc()

if(file.exists("/home/peter/Desktop/phd/evolutionaryComputation/Coine/expr.txt")==TRUE){
  file.remove("/home/peter/Desktop/phd/evolutionaryComputation/Coine/expr.txt")
  file.create("/home/peter/Desktop/phd/evolutionaryComputation/Coine/expr.txt")
}else{
  file.create("/home/peter/Desktop/phd/evolutionaryComputation/Coine/expr.txt")
}


itterationsNoImprove <- 0
best_so_far <- 0
monitorFunc <- function(result) {
  if(min(result$best$cost) < best_so_far){
    cat("new best", min(result$best$cost), "\n")
    best_so_far <<- min(result$best$cost)
    itterationsNoImprove <<- 0
  }else{
    itterationsNoImprove <<- itterationsNoImprove + 1
  }
  #if(result$population$currentIteration %% 50 == 0){
  #  cat("iteration", result$population$currentIteration, "Best of gen:", min(result$best$cost), "\n")
  #}
}



adaptive <- function(maxiter = 20){ #max iter defines the maximum multiple of initial mutationChance
  iter_small <- 100
  max_dep <- 10
  pops <- 100
  
  ge <- GrammaticalEvolution(grammarDef, fitness, terminationCost = -70, iterations = iter_small, max.depth = max_dep, popSize = pops, elitism = 0, monitorFunc = monitorFunc, optimizer = "ga")
  mutChan_init <- ge$settings$mutationChance
  
  totalMax <- 1000
  iter_total_max <- 1
  iter <- 1 #multiple of mutationChance
  while(iter < maxiter && ge$best$cost > -70 && iter_total_max < totalMax){
    mat <- t(ge$population$population[1:round(0.95*pops),])
    initPop <- split(mat, rep(1:ncol(mat), each = nrow(mat)))
    
    if(itterationsNoImprove >= iter_small){
      iter <- iter + 1
      mutChan <- iter*mutChan_init
      cat("no improvement for ", itterationsNoImprove, ", reruning search with higher mutation: ", mutChan, "\n")
    }else{
      iter <- 1
      mutChan <- mutChan_init
    }
    ge <- GrammaticalEvolution(grammarDef, fitness, terminationCost = -70, iterations = iter_small, max.depth = max_dep, popSize = pops, elitism = 0, monitorFunc = monitorFunc, optimizer = "ga", suggestions = initPop, mutationChance = mutChan)
    cat("iter_total ", iter_total_max, "\n")
    iter_total_max <- iter_total_max + 1
  }
  return(ge)
}

start.time <- Sys.time()
ge_res <- adaptive()
end.time <- Sys.time()


#cl <- makeCluster(6)
#clusterEvalQ(cl, library("gramEvol"))
#clusterEvalQ(cl, library("igraph"))
#clusterExport(cl, c("fitness","ABM","Nagents","entry_fee","th","penalty","append_file","make_empty_graph","V","addToLine"))
#ge <- GrammaticalEvolution(grammarDef, fitness, terminationCost = -70, iterations = 10, max.depth = 10, popSize = 300, elitism = 0, monitorFunc = monitorFunc, optimizer = "ga", suggestions = initPop )#, mutationChance = 100/(1+GetGrammarMaxSequenceLen(grammarDef, max.depth = 8)))#, plapply = function(...) parLapply(cl, ...))
#stopCluster(cl)




time.taken <- end.time - start.time
time.taken

buffer_stack <- read_file(path = "/home/peter/Desktop/phd/evolutionaryComputation/Coine/expr.txt")
plot(tail(sort(as.numeric(buffer_stack$fitness)),20), type = "l", main = "best 20 solutions")
```




## result analysis

```{r read}
buffer_stack1 <- read_file()
buffer_stack2 <- read_file(path = "/home/peter/Desktop/phd/evolutionaryComputation/Coine/expr.txt")
```

```{r analy}
plot(sort(as.numeric(buffer_stack2$fitness), decreasing = TRUE)[100:1], type = "l", main = "best 50 solutions", ylim = c(10,65))
lines(sort(as.numeric(buffer_stack1$fitness), decreasing = TRUE)[100:1], type = "l")
```

```{r test_Water}
tmp <- order(as.numeric(buffer_stack1$fitness), decreasing = TRUE)
strtmp <- strsplit(buffer_stack1$expr[tmp[1]], ",i")[[1]]
for(i in 2:length(strtmp)){
  strtmp[i] <- paste0('i',strtmp[i])
}
tmp_water <- parse(text = strtmp)
tmp_water
iterseq <- rep(FALSE, Nagents)
iterseq[c(1,2,10,10)] <- TRUE
ABM(tmp_water, writeToFile = FALSE, toplot = TRUE, iterseq = iterseq)
```

```{r test_array}
tmp <- order(as.numeric(buffer_stack2$fitness), decreasing = TRUE)
strtmp <- strsplit(buffer_stack2$expr[tmp[1]], ",i")[[1]]
for(i in 2:length(strtmp)){
  strtmp[i] <- paste0('i',strtmp[i])
}
tmp_array <- parse(text = strtmp)
tmp_array
iterseq <- rep(FALSE, Nagents)
iterseq[c(1,2,10,20)] <- TRUE
iterseq <- rep(TRUE, Nagents)
ABM(tmp_array, writeToFile = FALSE, toplot = TRUE, iterseq = iterseq)

```
```{r}
jpeg(filename="topos.jpg", width = 2*480, height = 480)
op <- par(mfrow=c(2,3))
iterseq <- rep(FALSE, Nagents)
iterseq[c(4,8,12)] <- TRUE
ABM(tmp_water, writeToFile = FALSE, toplot = TRUE, iterseq = iterseq)
ABM(tmp_array, writeToFile = FALSE, toplot = TRUE, iterseq = iterseq)
par(op)
dev.off()

```


--------------------------------------------------------------------------------------------------------------------------------------------

## Exhaustive Search

```{r exchaustive}
gc()
if(file.exists("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")==TRUE){
  file.remove("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")
  file.create("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")
}else{
  file.create("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")
}

monitorFunc <- function(result) {
  if(result$population$currentIteration %% 100 == 0){
    cat("iteration", result$population$currentIteration, "Best of gen:", min(result$best$cost), "\n")
  }
}

gex <- GrammaticalExhaustiveSearch(grammarDef, fitness, terminationCost = -50, max.depth = 6)#, monitorFunc = monitorFunc)
gex
```

## Exhaustive Search

```{r exchaustive}
gc()
if(file.exists("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")==TRUE){
  file.remove("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")
  file.create("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")
}else{
  file.create("/home/peter/Desktop/phd/evolutionaryComputation/Coine/exprFile.txt")
}

monitorFunc <- function(result) {
  if(result$population$currentIteration %% 100 == 0){
    cat("iteration", result$population$currentIteration, "Best of gen:", min(result$best$cost), "\n")
  }
}

gex <- GrammaticalExhaustiveSearch(grammarDef, fitness, terminationCost = -5000, max.depth = 5)#, monitorFunc = monitorFunc)
gex
```

## Grammatical Evolution penalized

```{r penalized}
#threshold stack
#stack_expr <- safe_beffer_stack$stack[tail(order(as.numeric(safe_beffer_stack$fitness)),6)]
#buffer_stack <- data.frame("stack" = NA, "fitness" = NA)


buffer_stack <- read_file()
stack_expr <- buffer_stack$expr[which(buffer_stack$fitness > mean(buffer_stack$fitness) + sd(buffer_stack$fitness))]


cl <- makeCluster(8)
clusterEvalQ(cl, library("gramEvol"))
clusterExport(cl, c("fitness","ABM","Nagents","entry_fee","th","penalty","send","addUser","removeUser","getBalance","append_file","stack_expr"))
ge_penalized <- GrammaticalEvolution(grammarDef, fitness, terminationCost = -5000, iterations = 1000, max.depth = 5, popSize = 32, elitism = 4, monitorFunc = monitorFunc, plapply = function(...) parLapply(cl, ...))
stopCluster(cl)


# higher mutation seems to screew thisngs up

ge_penalized
```


## deployment and testing of the screening



```{r plot}
data <- data.frame(
  agent=1:Nagents,
  percentage=colMeans(tmpM),
  upperQ = matrixStats::colQuantiles(tmpM, probs = 0.80),
  lowerQ = matrixStats::colQuantiles(tmpM, probs = 0.20),
  basicPonzi = sort(ponziCases$BasicPonzi),
  arrayPS = sort(ponziCases$ArrayPS),
  waterfallScheme = sort(ponziCases$WaterfallScheme),
  handoverScheme = sort(ponziCases$HandoverScheme)
)
# Most basic error bar
p <- ggplot(data) +
    geom_bar( aes(x=agent, y=percentage), stat="identity", fill="skyblue", alpha=0.8) +
    geom_errorbar( aes(x=agent, ymin=lowerQ, ymax=upperQ), width=0.4, colour="orange", alpha=0.6, size=1.2) + 
    geom_line(aes(x=agent, y=arrayPS, colour = "Array")) +
    geom_line(aes(x=agent, y=waterfallScheme, colour = "Waterfall")) +
    ggtitle(paste0("mean gain/loss percentange distribution for the best ",n_best," contracts \nwith 20% upper/lower qunatile")) 

p
ggsave("distribution.png")
```

```{r findScheme}
tmp <- which.min(abs(buffer_stack$fitness - ABM(WaterfallScheme, FALSE)))
parse(text = buffer_stack$expr[tmp])


```